Carrier phase and amplitude estimation for phase shift keying using pilots and data

### 2014-07-03 responses/proofcorrection.tex
added more changes.  Past the sectioning error on page 7 now.

@@

>>>>

\item Page 4, column 2.  The phrase ``the loops on lines 1 and II'' the II should be 11 (the number eleven rather than two capital I's).  That is, ``the loops on lines 1 and 11''.

\item Page 5, column 1.  The phrase ``to denote $x$ taken `~modulo $2\pi$' into the interval \dots''.  There is a space between the apostrophe and the word modulo.  That is `~modulo $2\pi$' shoud be `modulo $2\pi$'.

\item Page 6, column 1, start of section 4.  The first equation starting $LS(\rho, \theta) = \dots$ has the word `where' placed in the middle of the column.  The word `where' should be left justified rather than centered.  It should look like:
 \begin{align*}
LS(\rho, \theta) &=\sum_{i \in P} \abs{ y_i - \rho e^{j\theta} p_i }^2 + \sum_{i \in D} \abs{ y_i - \rho e^{j\theta} \hat{d_i}(\theta) }^2 \\
&= A - \rho Z(\theta) - \rho Z^*(\theta) + L \rho^2,
\end{align*}
where
\[
Z(\theta)  = \sum_{i \in P} y_i e^{-j\theta} p_i^* + \sum_{i \in D} y_i e^{-j\theta} \hat{d}_i^*(\theta),
\]

\item Page 6 column 2 second last equation starting $Z(\theta) = \dots$.  The equation ends with a full stop.  The full stop is put into the superscript of the equations, but it should not be.  It should look like:
\[
Z(\theta) = \rho_0 \sum_{i \in P} R_i e^{j(\lambda + \Phi_i)} + \rho_0  \sum_{i \in D} R_i e^{j\sfracpart{\lambda + \Phi_i}}.
\]

@@

\item
